---
title: "UseCase"
author: "Paul Deveau"
output: 
  html_document: 
    highlight: tango
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DevGRaph)
```

#Getting started with DevGRaph

This vignette describes possibilities for the package DevGRaph with the toy example given in the package.

## Setting up the files for analysis
This package was developped to ease package development. For this reason, it will source R script files from a unique folder.
In this vignette the files are located in `inst/extdata`.
```{r path_setup}
 path<-system.file("extdata", package = "DevGRaph")

```

In addition, user can provide information on the state of a function with the gTag.
A gTag is a tag that can be added to the function corpus as a comment with following syntax:
`#'gTag status`
The status of the function will then be represented by a color in the different graphs.

The following statuses are currently available:

````{r status,echo = FALSE}

knitr::kable(data.frame(Status = c("unkown (default)","complete","undocumented","ongoing"),Color = c("grey","green","red","orange")))


````


##Viewing all functions from package

`DevGraphLab` is a function designed to show all interactions between functions of the graph. Each panel represents an independant cluster of functions. This is a wrap-up function that calls `GraphLab` to analyze the scripts, looks for independant clusters and plots each one of them with `PlotGraphLab`. 

```{r dev}

DevGraphLab(path = path)

```

We can here see that two interaction clusters coexist: one containing a single function `Outsider` and one starting with `Start`.

##Zooming on a specific function

First we need to analyze the collection of scripts with `GraphLab`.

```{r Graph}
Graph<-GraphLab(path = path)
```

The graph object is a list of three elements: `Functions` (a list of data frames), `interaction`, and `status`.
`interaction` is a binary matrix with a 1 if the function from the column calls the function from the row. Below we show the last two columns of the interaction matrix of the toy example.

```{r interaction_show, echo = TRUE}
knitr::kable(Graph$interaction[,c("Start","progeny")])
```

We can see that `Start` calls all function but `calls_ggplot2_function`, `recursive`, and `Start` itself.


If we wanted to plot the interaction of `Start` with its successive progenies, we would write:

```{r PlotGraph_1}
PlotGraphLab(GraphLab = Graph,func = "Start")

```

We can also chose to filter out the packages from which imports are listed. By default, "base" and "utils" packages are hidden from the plots. To show them, we can use:
```{r PlotGraph_2}
PlotGraphLab(GraphLab = Graph,func = "Start",filterOut = "")

```

And to hide another package, for example ggplot2:
```{r PlotGraph_3}
PlotGraphLab(GraphLab = Graph,func = "Start",filterOut = c("base","utils","ggplot2"))

```

##Show conflicting function names from two packages

We show conflicts of function names for packages that are loaded in the environment.
Let's focus on `Outsider` and its calls:

```{r PlotGraph_4}
PlotGraphLab(GraphLab = Graph,func = "Outsider",filterOut = "")

```

We can see here that `rbind` that was previously masked as being part of `base` package is now shown and belongs to two packages: `methods` and `base`.

##Changing parameters
###Changing the dictionnary

For convenience, the tags can be changed with a dictionnary, either because the project requires different tags, or simply to change the colors of the plot.
For example to edit the colors of the default dictionnary

```{r DictEx}
PlotGraphLab(GraphLab = Graph,func = "Start",dictionnary = c(complete = "seagreen", ongoing="gold", undocumented = "purple"))

```

As shown here, the `unknown` parameter is not required for the dictionnary, but one can use it nonetheless to change the color used to display function with unknown tags (either missing or unrecognized).

```{r UnknownTag}
PlotGraphLab(GraphLab = Graph,func = "Start",dictionnary = c(complete = "seagreen",ongoing ="gold", undocumented = "purple", unknown = "skyblue"))

```

###Changing box color
The color of the outer box can be modified with the `color` parameter, as shown below

```{r color}
PlotGraphLab(GraphLab = Graph,func = "Start",color = "white")

```

###Changing arrow curvature

Sometimes, for readability, it can be useful to straighten arrows, this can be setting `arrow_curv` to zero:
```{r arrow_curv}
PlotGraphLab(GraphLab = Graph,func = "Start",arrow_curv = 0)

```

By default, the curvature is set to -0.2.

###Passing plot arguments to `DevGraphLab`

All these arguments can be passed to `DevGraphLab` to edit the plot in the same manner as one would do with `PlotGraphLab`.

```{r dev_edited}

DevGraphLab(path = path,dictionnary = c(complete = "seagreen",ongoing ="gold", undocumented = "purple", unknown = "skyblue"),arrow_curv = 0 , color = "grey40")

```
